%% Beginning of the `template.tex' file.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work can be distributed or modified under the 
% conditions of the LaTeX Project Public License V1.3c, 
% available at http://www.latex-project.org/lppl/.
%
% Translation to Spanish by Fausto M. Lagos (piratax007@protonmail.ch), 2016.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible font size options ('10pt', '11pt' and '12pt'), paper ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv styles
\moderncvstyle{casual}                             % Available styles are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options are 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % uncomment to set the default font; use '\sfdefault' for sans serif by default, '\rmdefault' for roman, or any other font name installed on your system
%\nopagenumbers{}                                  % uncomment to remove automatic page numbering for multi-page letters

% Character encoding
\usepackage[utf8]{inputenc}                        % If not using xelatex or lualatex, replace with the encoding you're using


% Margin configuration
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % uncomment if you want to adjust the width of the date column
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, to force the name width. The length is normally calculated to avoid overlaps with personal information; uncomment this line at your own risk

% Personal Information
\name{Kelvin}{Le}
\title{Resume Title}                               % optional, remove or comment if you don't want your personal title to appear
% optional, remove or comment if you don't want location data; postal code and country can be omitted or left blank
          % optional, remove or comment if you don't want to include your fax number
\email{kelvin.minhle1002@gmail.com}                               % optional, remove or comment if you don't want to include your email address
\homepage{www.johndoe.com}                         % optional, remove or comment if you don't want to include your website


% to show numerical labels in bibliography (by default, no labels are shown); uncomment the following lines only if you're using bibliographic references in your letter
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]} % Consider replacing line 44 with this one

% Bibliography with multiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% Recipient's details
\recipient{Rio Tinto}{Brisbane, QLD 4000}
\date{\today}
\opening{Dear Recruitment Team,}
\closing{Sincerely,}
\enclosure[Attachments]{Title of the Attachments}          % optional, remove or comment if no attachments are included 
\makelettertitle

Australia is renowned for being a global hub for the energy and mining industries, 
known for its innovation and advanced technology in production processes. 
Through my in-depth research into the undergraduate opportunities within these industries, 
including attending career fairs and engaging with company representatives, 
Rio Tinto has stood out to me as a leader in the field due to the global scale of its operations 
and its strong commitment to sustainability and innovation.


As an undergraduate \textbf{Mechatronics/Aerospace student},
 I bring proven technical skills at the intersection of robotics, computer science, systems engineering,
 and electrical engineering. I have always been highly interested in the opportunity to contribute to Rio Tinto’s 
 innovative work in robotics and mining through this internship position.

I am writing to express my enthusiastic interest in the intern position at \textbf{Rio Tinto}. As an Undergraduate \textbf{Mechatronics/Aerospace Student}, everyone tells me that working at 
the intersection of robotics, computer science and electrical is going to be massive. However, I am 


Recently, I optimized a robotic system for a autonomous car
, improving its efficiency by 20\%. 
I’m eager to bring this hands-on experience to Rio Tinto, leveraging my technical expertise and 
problem-solving mindset to drive innovation in your operations. 
I would love the opportunity to contribute to your team.


I am writing to express my enthusiastic interest in the intern position at \textbf{Rio Tinto}, 
as an undergraduate student studying \textbf{Mechatronics/Aerospace Engineering} at the QUT. The degree brings me with a solid foundation in Mechanical/Electrical 
and the thing that I am passionate about is Robotics/Automation. I am excited about the opportunity to contribute to the innovative work that your team is doing in the field of robotics.

Passion and enthusiasm for robotics have driven me to pursue a degree in Mechatronics/Aerospace Engineering. I have developed a strong foundation in mechanical and electrical engineering principles, as well as programming skills in languages such as Python, C++, and MATLAB. I have also gained practical experience through internships and projects, where I have worked on a wide range of projects, including [specific examples of relevant experience]. My ability to [key skills related to the position] has allowed me to contribute effectively to past teams and achieve [specific outcomes]. I am excited about the opportunity to bring my [skills] to Rio Tinto and contribute to its continued success. 
And it will never be enough to describe my .


I have worked on a wide range of projects, including [specific examples of relevant experience]. 
My ability to [key skills related to the position] has allowed me to contribute effectively to past teams and achieve [specific outcomes]. 
I am excited about the opportunity to bring my [skills] to [Company Name] and contribute to its continued success.

I would welcome the opportunity to discuss my qualifications further and explore how I can contribute to the success of your team. Thank you for considering my application.

\makeletterclosing

\end{document}
